Hydrodynamics of a Semipermeable Inextensible Membrane Under Flow and Confinement

### 2021-04-30 vesicle_code/docs/permeableVes/semipermeable_vesicle.tex
worked on Fig 7

\begin{figure*}[htp]
  \centering
  \ifTikz
  \input{figures/parabolicComposite.tikz}
  \else
  \includegraphics{figures/parabolicComposite.pdf}
  \fi
  \caption{\label{fig:parabolicComposite} (a) The equilibrium shape of
  a semipermeable inextensible membrane submerged in a Poiseuille flow with varying
  initial reduced areas and flow rates. The red regions correspond to
  influx and the blue regions correspond to efflux. (b) The steady
  state vertical displacement at four different flow velocities. The
  steady state shapes are superimposed. (c) The reduced area of the
  slipper formed with the flow rate of $800 \; \mu$m/s. (d) The membrane
  shape shown with the background imposed flow. The channel width is
  12.5 times larger than the vesicle radius. The corresponding reduced
  area of each membrane shape is indicated by the marks in plot (c).}
\end{figure*}

>>>>

\begin{figure*}[htp]
  \centering
  \ifTikz
  \input{figures/parabolicComposite.tikz}
  \else
  \includegraphics{figures/parabolicComposite.pdf}
  \fi
  \caption{\label{fig:parabolicComposite} (a) A semipermeable membrane
  suspended in a Poiseuille flow with maximum velocity $800 \; \mu$m/s.
  The channel width is 12.5 times larger than the vesicle radius. (b)
  The reduced area of the vesicle as a function of time. The red marks
  correspond to the vesicle shapes in (a). (c) The equilibrium shape of
  a semipermeable inextensible membrane submerged in a Poiseuille flow
  with varying initial reduced areas and flow rates. The red regions
  correspond to influx and the blue regions correspond to efflux. (d)
  The steady state vertical displacement at four different flow
  velocities.}
\end{figure*}
